\documentclass{article}
\usepackage{titlesec,soulutf8}
\renewcommand{\thesection}{\Roman{section} }
\renewcommand{\thesubsection}{\arabic{subsection}}
\titleformat{\section}
{\normalfont\bfseries\filcenter}{ARTICLE \thesection:}{1em}{}
\titleformat{\subsection}
{\normalfont}{\ul{Section \thesubsection. \enspace}}{0em}{\ul}
\begin{document}
\title{AMENDED \& RESTATED \\ \hfill \\ BY-LAWS \\ \hfill \\ OF \\ \hfill \\ REGEN FOUNDATION}
\author{ Adopted: May 31st, 2023}
\date{} 
\maketitle
\clearpage
\tableofcontents
\clearpage
\section{NAME, PURPOSES, OFFICE}
\subsection{Name}
The name of the Corporation is Regen Foundation (the “Corporation”).
\subsection{Purposes}
  The purposes and powers of the Corporation shall be those set forth in the Certificate of Incorporation.
\subsection{Office}
  The initial office of the Corporation shall be located at 251 Little Falls Drive, Wilmington, in the county of New Castle, in the State of Delaware.  The Corporation may change the location of the office or maintain additional offices at such other places as the Board of Directors may from time to time determine.
\section{MEMBERS}
\subsection{Membership Criteria}
\begin{itemize}
\item Organizational history of commitment to domain-relevant activities $($such as regenerative agriculture, remote sensing, ecology, earth systems, blockchain, or regenerative economics$)$
\item Transparency around legal and financial relationships
\item Agreement to at least quarterly remote meetings with other consortium members and participation in a transparent and online voting and governance in which members will lose reputation and eventually be removed from the consortium if not participating
\item Agreement to send a representative to the annual consortium meeting that is hosted by Regen Foundation
\item Signature of agreement to Regen Consortium Member Agreement
\end{itemize}
\subsection{Members}
The membership body of the Corporation is called Regen Consortium (the “Consortium”). The membership class is organizational as opposed to individual. The Consortium shall have nine (9) initial members, to be determined by a resolution of the Board or an amendment to these By-laws. 

Subsequent members must pre-qualify via the membership criteria in Section 2.1. Pre-qualified candidates may be voted in by a two-thirds vote of the existing membership.
\subsection{Term, Resignation, and Removal}
The term of membership shall be life.  Notwithstanding the foregoing, any member, after having fulfilled all obligations to the Corporation, may resign by written notice to the Secretary of the Corporation. Any member may be removed at any time with or without cause by two-thirds vote of all of the members.
\subsection{Meetings}
A meeting of the members of the Corporation shall be held annually for the transaction of such other business.  Special meetings of the members may be called by any member.
\subsection{Notice}
Notice of meetings shall be given personally or sent by mail, e-mail or other electronic means, or facsimile transmission to each member by the Secretary, addressed to the organization at its address as it appears on the books and records of the Corporation, at least ten (10) days before the day on which the meeting is to be held.  Such notice shall state the date and hour when and place where the meeting is to be held, and to the extent possible, the purpose or purposes for which the meeting is called.  Unless it is an annual meeting, such notice shall indicate that it is being issued by or at the direction of the entity or entities calling the meeting.  Notice of any adjournment of a meeting of the members to another time or place shall be given to any members who were not present at the time of the adjournment.  No notice of any meeting of the members need be given to any member who attends such meeting without protesting prior to or at the commencement of the meeting the lack of notice of such meeting, or to any member who submits a signed waiver of notice whether before or after the meeting.
\subsection{Quorum and Voting}
At all meetings of the members the presence in person of a majority of the members shall be necessary and sufficient to constitute a quorum. Except as otherwise provided by law or by these By-laws, the act of a majority of the members shall be the act of the members. In the absence of a quorum, a majority of the members present, without notice other than by announcement at the meeting, may adjourn the meeting until a quorum shall attend. Members may send multiple representatives to meetings, but each member shall only have one (1) vote. Each member entitled to vote at a meeting or to express consent to a corporate action in writing without a meeting may authorize another person or persons to act for such member by proxy, but no such proxy shall be voted or acted upon after three years from its date, unless the proxy provides for a longer period. A proxy shall be irrevocable if it states that it is irrevocable and if, and only as long as, it is coupled with an interest sufficient in law to support an irrevocable power. A member may revoke any proxy which is not irrevocable by attending the meeting and voting in person or by delivering to the secretary of the Corporation a revocation of the proxy or a new proxy bearing a later date. Voting at meetings of members need not be by written ballot.
\subsection{Actions in Writing}
Any action required or permitted under these By-laws to be taken by the members or by any committee thereof may be taken without a meeting if a majority of the members consent in writing to the adoption of a resolution authorizing the action. In accordance with Section 215 of the Delaware General Corporation Law (“DGCL”), such consent may be provided by electronic transmission, including by use of the Loomio decision-making software and web service platform. Pursuant to Section 228 of the DGCL, no consent shall be effective to take the corporate action at issue unless a majority of the members provide written consent to take such action and such consents are delivered to the Corporation within sixty (60) days of the first date on which a consent is so delivered to the Corporation. Members may instruct the Corporation that their consent is effective at a future time (but not later than sixty (60) days after instruction is given by the Corporation) or conditioned upon an event happening. Such consent is revocable prior to becoming effective.
\subsection{Remote Participation}
Any one or more members may participate in a meeting of the members by means of a conference telephone or similar communications equipment allowing all persons participating in the meeting to hear each other at the same time.  Participation by such means shall constitute presence in person at a meeting.
\section{BOARD OF DIRECTORS}
\subsection{Power and Number}
The Board of Directors shall have general power to control and manage the affairs and property of the Corporation in accordance with the purposes and limitations set forth in the Certificate of Incorporation and as set forth in these By-laws.  The initial Board of Directors shall be appointed by the Incorporator named in the Certificate of Incorporation, and each person so appointed shall serve as Director until the first meeting of the members.  Thereafter, the Board of Directors of the Corporation shall consist of such number of persons as determined from time to time by the members. Beginning three years after the formation of the Corporation, a board seat will come up for appointment each year. External seats will come up for appointment first. Appointments from year four forward will be determined by the Consortium. The number may be increased or decreased by amendment of the By-laws, but no decrease shall shorten the term of any incumbent Director.
\subsection{Election, Term}
The initial Board of Directors shall serve for a period of three (3) years or until his or her death, resignation or removal, and until his or her successor has been elected and qualified. Thereafter, one (1) non-founding Director shall be replaced annually by an election by a majority of the members or by a majority of the entire Board or by action in writing signed by all of the Directors, subject to approval of the election by a vote of the majority of the members. Subsequent to the fourth annual meeting and Board votes, the Consortium shall determine which Directors shall be eligible for replacement. A duly elected Director selected by the Consortium after the fourth annual meeting will hold office for a term of five (5) years or until his or her death, resignation or removal, and until his or her successor has been elected and qualified.
\subsection{Vacancies}
In the first three years, if any vacancy shall occur in the Board of Directors for any cause, including an increase in the number of Directors, the vacancy may be filled by a duly adopted resolution of all existing directors. From year four forward, vacancies may be filled by a duly adopted resolution of  two-thirds of the members at a meeting at which quorum is present.
\subsection{Removal}
Any Director may be removed at any time, with or without cause and with or without notice, by a unanimous vote of other Directors by action in writing signed by all of the other Directors.
\subsection{Resignation}
Any Director may resign from office at any time by delivering a resignation in writing to the President.  Acceptance of the resignation, unless required by its terms, shall not be necessary to make the resignation effective.
\subsection{Director Stipend}
Director currently receive no stipend. Any future changes to such stipend will require Consortium approval.
\section{MEETINGS OF DIRECTORS}
\subsection{Meetings}
Meetings of the Board of Directors, annual, regular or special, may be held at any day, and at such time and place, as shall be determined by the Board of Directors.
\subsection{Special Meetings}
Special meetings of the Board of Directors shall be called at any time by the Secretary upon the request of the President or of any Director.  Each special meeting of the Board of Directors shall be held at such place as shall be specified in the notice of such meeting or waiver thereof.
\subsection{Notice of Meetings}
Notice of meetings shall be given personally or sent by mail, e-mail or other electronic means, or facsimile transmission to each Director, addressed to him or her at his or her address as it appears on the books and records of the Corporation, at least three (3) days before the day on which the meeting is to be held.  Such notice shall state the time when and place where the meeting is to be held, and to the extent possible, the purpose or purposes for which the meeting is called.  Notice of any adjournment of a meeting of the Board of Directors to another time or place shall be given to any Directors who were not present at the time of the adjournment.  No notice of any special meeting of the Board of Directors need be given to any Director who attends such special meeting without protesting prior to or at the commencement of the special meeting the lack of notice of such special meeting, or to any Director who submits a signed waiver of notice whether before or after the special meeting.
\subsection{Quorum, Voting}
At all meetings of the Board of Directors the presence in person of a majority of the Directors shall be necessary and sufficient to constitute a quorum.  Except as otherwise provided by law or by these By-laws, the act of a majority of the Directors present at a meeting of the Board of Directors at which a quorum is present shall be the act of the Board of Directors, subject to veto by the sole member.  In the absence of a quorum, a majority of the Directors present, or if no Director is present, any officer entitled to preside at, or act as Secretary of, such meeting, without notice other than by announcement at the meeting, may adjourn the meeting from time to time, for a period of not more than thirty (30) days at any one time, until a quorum shall attend.
\subsection{Actions in Writing}
 Any action required or permitted under these By-laws to be taken by the Board of Directors or by any committee thereof may be taken without a meeting if all members of the Board of Directors or the committee consent in writing to the adoption of a resolution authorizing the action.  The resolution and the written consents thereto by the members of the Board of Directors or committee shall be filed with the minutes of the proceedings of the Board of Directors or the committee.
\subsection{Remote Participation}
Any one or more members of the Board of Directors or any committee thereof may participate in a meeting of the Board of Directors or such committee by means of a conference telephone or similar communications equipment allowing all persons participating in the meeting to hear each other at the same time.  Participation by such means shall constitute presence in person at a meeting.
\subsection{Annual Report}
At an annual meeting of the Board of Directors, the Treasurer shall present a report, verified by the President and the Treasurer or by a majority of the Directors, or certified by an independent public accounting firm, showing in appropriate detail:  (1) the assets and liabilities of the Corporation as of a 12-month fiscal period terminating not more than six months prior to the meeting, (2) the principal changes in assets and liabilities during the fiscal period, (3) the revenues or receipts of the Corporation for that fiscal period, and (4) the expenses or disbursements of the Corporation during said fiscal period.  Such report shall be filed with the records of the Corporation and a copy thereof entered in the minutes of the proceedings of the annual meeting.  The report to the Board may consist of a verified or certified copy of any report by the Corporation to the Internal Revenue Service or any relevant Attorney General that includes the information herein above specified.
\section{EXECUTIVE COMMITTEE AND OTHER COMMITTEES}
\subsection{Appointment, Powers}
The Board of Directors may, by resolution duly adopted, appoint an Executive Committee consisting of three (3) or more Directors and other standing committees.  Each Committee shall have and may exercise during the intervals between meetings of the Board of Directors, to the extent provided by the resolution establishing it, all of the powers of the Board of Directors in the management and control of the charitable activities, property, business and affairs of the Corporation which are not specifically required by law or by these By-laws to be exercised by the full Board, except that it shall have no power as to the following matters:
\renewcommand{\labelenumi}{\alph{enumi}$)$}
\begin{enumerate}
\item the submission to members of any action requiring member approval;
\item the filling of vacancies in the Board of Directors or in any committee;
\item the removal of Directors from office;
\item the alteration of the number of Directors;
\item the fixing of compensation of the Directors for serving on the Board or on any committee;
\item the authorization of indemnification for expenses;
\item the amendment of the Certificate of Incorporation;
\item the amendment or repeal of the By-laws or the adoption of new By-laws; and
\item the amendment or repeal of any resolution of the Board of Directors that by its terms shall not be so amendable or repealable.
\end{enumerate}
\subsection{Other Committees}
Special Committees may be appointed by the President with the consent of the Board and shall have only the powers specifically delegated to them by the Board and in no case shall have powers which are not authorized for standing committees under this Article V.  At least one member of such a committee shall be a member of the Board of Directors, but otherwise the members of such committees need not be Directors of the Corporation.
\subsection{Term}
Each member of the Executive Committee or other committee shall be and remain a member thereof and shall hold office until his or her successor shall have been appointed, or until his or her death or resignation, or until he or she shall have been removed in the manner hereinafter provided.
\subsection{Removal}
Any member of the Executive Committee or other committee may be removed at any time, with or without cause and with or without notice, by a majority of all of the Directors at any meeting of the Board of Directors or by action in writing signed by all of the Directors, subject to approval of the removal by vote of the majority of the members at a meeting at which quorum is present.  The Board of Directors may, by a resolution duly adopted at any meeting, dissolve the Executive Committee or other committee.
\subsection{Vacancies}
If any vacancy shall occur in the Executive Committee or other committee for any reason, including an increase in the number of members of such committee, the vacancy may be filled at any meeting of the Board of Directors.
\subsection{Meetings, Notice}
The Executive Committee or other committee may hold meetings at such time or times and at such place or places as it shall determine from time to time.  Notice of every meeting shall be given personally or sent by mail, e-mail or other electronic means, or facsimile to each member of the Executive Committee or other committee, addressed to him or her at his or her address as it appears on the books or records of the Corporation, at least three (3) days before the day on which the meeting is to be held.  Such notice shall state the time when and place where the meeting is to be held, and to the extent possible, the purpose or purposes for which the meeting is called.  No notice of any meeting of the Executive Committee or other committee need be given to any member who attends such meeting without protesting prior to or at the commencement of the meeting the lack of notice of such meeting, or to any member who submits a signed waiver of notice whether before or after the meeting.  The Executive Committee or other committee shall keep a record of its proceedings.
\subsection{Quorum, Vote}
At all meetings of the Executive Committee or other committee, the presence in person of members constituting a majority of the membership of the entire Executive Committee or other committee, but in no event less than two (2) members, shall be necessary and sufficient to constitute a quorum, and except as otherwise provided by law or by these By-laws, the act of a majority of the members present shall be the act of the Executive Committee or other committee.
\section{OFFICERS}
\subsection{Elected Officers}
The elected officers of the Corporation may include a President, one or more Vice Presidents, a Secretary, a Treasurer and such other officers as the Board of Directors may from time to time elect.  The officers may, but need not, be members of the Board of Directors.  One person may hold any two or more of said offices, except that the office of President cannot be held by the same person who holds the office of Secretary.
\subsection{Election, Removal, Vacancies}
The elected officers shall be elected for a term of one (1) year at the annual meeting of Directors immediately following the election of Directors.  Each such officer shall hold office until the next annual meeting of Directors or until a successor shall have been elected and shall qualify, or until his or her death or resignation, or until he or she shall have been removed.  Any elected officer may be removed at any time, with or without cause and with or without notice, at a meeting by a majority of all the Directors of the Corporation, subject to the approval of the removal by a majority of the members at a meeting at which quorum is present.  A vacancy in any elective office may be filled by the Directors at any meeting.
\subsection{President}
The President shall exercise general supervision over the affairs of the Corporation, subject, however, to the control of the Board of Directors and the Executive Committee, if any.  The President shall keep the Board of Directors fully informed about the affairs of the Corporation.  The President shall preside at all meetings of the Board of Directors and of the Executive Committee, if any, and in general shall perform all duties incident to the office of President of the Corporation and such other duties as from time to time may be assigned to him or her by the Board of Directors or by the Executive Committee, if any.
\subsection{Vice President}
The Vice President (or if there is more than one Vice President, a Vice President designated by the Board of Directors) shall, in the temporary absence or disability of the President, act in the place of the President, or, if there shall be no Vice President, the President’s duties shall be performed by the individual Director designated by the Board of Directors, or, in the absence of such designation, the individual Director designated by the President.  The Vice President, if any, shall also perform such other duties as from time to time may be assigned to him or her by the Board of Directors, the President or the Executive Committee, if any, which duties may include powers elsewhere assigned or delegated to other officers.
\subsection{Secretary}
The Secretary shall keep the minute books and seal of the Corporation, serve or cause to be served all notices of the Corporation, including notices of meetings of the Board of Directors, record the minutes of the meetings of the Board of Directors, and in general perform all duties incident to the office of Secretary and such other duties as from time to time may be assigned to him or her by the Board of Directors, the President or the Executive Committee, if any, which duties may include powers elsewhere assigned or delegated to other officers.
\subsection{Treasurer}
The Treasurer shall have custody of all funds and property owned by the Corporation and shall keep full and accurate account of all receipts and disbursements.  The Treasurer shall deposit all moneys and other valuable effects in the name and to the credit of the Corporation in such depositories as may be designated by the Board of Directors and shall render to the President and Directors at the regular meetings of the Board of Directors, or whenever they may require it, an account of all of his or her transactions as Treasurer and of the financial condition of the Corporation and shall exhibit to such persons at all reasonable times the books and accounts of the Corporation and shall perform all duties incident to the office of the Treasurer and such other duties as from time to time may be assigned to him or her by the Board of Directors, the President, or the Executive Committee, if any, which duties may include powers elsewhere assigned or delegated to other officers.
\subsection{Other Agents, Advisors and Employees}
The Board of Directors may from time to time appoint such agents, advisors and employees as it shall deem necessary, each of whom shall hold office at the pleasure of the Board of Directors, and shall have such authority, perform such duties and receive such reasonable compensation, if any, as the Board of Directors may from time to time determine.
\section{COMPENSATION OF DIRECTORS AND OFFICERS}
\subsection{Authorization}
No Director of the Corporation shall receive directly or indirectly any salary, compensation or emolument from the Corporation, as a Director, unless:
\begin{enumerate}
\item authorized at a meeting of the Board of Directors at which a quorum is present, by the concurring vote of a majority of the disinterested Directors present at such meeting; and
\item approved by a vote of a majority of the Consortium.
\end{enumerate}
No officer of the Corporation shall receive directly or indirectly any salary, compensation or emolument from the Corporation, as an officer or otherwise (except as a Director), unless authorized at a meeting of the Board of Directors at which a quorum is present, by the concurring vote of a majority of the disinterested Directors present at such meeting.
\subsection{Interested Parties}
No contract, agreement or transaction to which the Corporation is or may be a party shall be invalidated or in any way impaired by reason of the fact that any Director or officer is directly or indirectly interested therein.
\subsection{Loans}
No loans shall be made by the Corporation to any of its Directors, officers or their respective family members or to any entity in which one or more of its Directors, officers or their respective family members holds a financial interest.
\section{FINANCIAL AUTHORITY}
\subsection{Books and Records}
There shall be kept at the office of the Corporation correct books of account of the activities and transactions of the Corporation, including a minute book, which shall contain a copy of the Certificate of Incorporation, a copy of these By-laws, and all minutes of meetings and unanimous written consents of the Board of Directors.
\subsection{Execution of Instruments}
The Board of Directors, or the Executive Committee, if any, is authorized to select the banks or depositories it deems proper for the funds of the Corporation.  The Board of Directors shall determine who shall be authorized from time to time and in what manner on the Corporation’s behalf to sign checks, drafts or other orders for the payment of money, acceptance, notes or other evidences or indebtedness, to enter into contracts or to execute and deliver other documents and instruments.
\subsection{Investments}
The funds of the Corporation may be retained in whole or in part in cash or invested and reinvested from time to time in such property, real, personal or otherwise, including stocks, bonds or other securities, as the Board of Directors may deem desirable.
\section{INDEMNIFICATION}
The Corporation may, to the fullest extent now or hereafter permitted by and in accordance with the standards and procedures provided for by Section 145 of the General Corporations Law and any amendments thereto, indemnify any person made, or threatened to be made, a party to any action or proceeding by reason of the fact that he or she, or his or her testator or intestate, is or was a member, Director, officer, employee or agent of the Corporation, or of any other organization served by him or her in any capacity at the request of the Corporation, against judgments, fines, amounts paid in settlement and reasonable expenses, including attorneys’ fees, actually and necessarily incurred by him or her in connection with such action or proceeding.
\section{FISCAL YEAR}
The fiscal year of the Corporation shall be determined by the Board of Directors.
\section{EXECUTION OF INSTRUMENTS}
All documents, instruments or writings of any nature shall be signed, executed, and delivered by such officers, agents or employees of the Corporation, and in such manner, as from time to time may be determined by the Board of Directors.
\section{AMENDMENTS}
The By-laws of the Corporation shall be subject to alteration or repeal, and new By-laws may be made, by the affirmative vote of two thirds of the members or the affirmative vote of a majority of the Board of Directors, except that any amendment which increases the quorum requirement or the proportion of votes necessary for the transaction of business or of any specified item of business must be authorized by a vote of two-thirds of the members or Board of Directors, subject to member approval.
\end{document}