\documentclass{article}
\begin{document}
\title{FINANCIAL MANAGEMENT POLICY \protect\\ OF \protect\\ REGEN FOUNDATION}
\author{Adopted: March 3rd, 2021}
\date{} 
\maketitle
\begin{enumerate}
\item The financial management of Regen Foundation will serve its charitable cause
\item Division of Responsibilities
\begin{enumerate}
\item The Board of Directors of Regen Foundation are responsible for monitoring the financial status of the organization and identifying and securing resources for the organization, including:
\begin{enumerate}
\item Review and approve annual operating budget
\item Review quarterly financial statements
\item Review Executive Director performance and establish salary
\item Ensuring compliance with the Uniform Prudence Management of Institutional Funds Act
\end{enumerate}
\item Executive Director
\begin{enumerate}
\item Role: To maintain oversight of the financial condition of the organization and develop annual fundraising plans
\item Reporting: The Executive Director reports to the Board of Directors
\item The Executive Director is responsible for the day-to-day financial management and accounting of the organization, including:
\begin{enumerate}
\item Review and approve all financial reports, including cash flow projections
\item Development of the annual budget
\item Monitor program budgets
\item Review and manage cash flow
\item Monthly review of financial position to Board of Directors
\end{enumerate}
\end{enumerate}
\item The Executive Director (or accountant) is responsible for:
\begin{enumerate}
\item Data entry and integrity of accounting system
\item Review all invoices
\item Process all invoices and prepare checks for signatures
\item Make bank deposits, where applicable
\item Review and process payroll 
\item Maintain general ledger
\item Prepare monthly and year-end financial reports
\item Monitor grant reporting and investor funding and use of restricted funds
\item Reconcile all bank accounts
\item Mail vendor checks, where applicable 
\item Manage Accounts Receivable, Accounts Payable
\end{enumerate}
\end{enumerate}
\item Financial Policies
\begin{enumerate}
\item Bank Account Policy 
\begin{enumerate}
\item As of January 26th, 2021, Regen Foundation holds one non-profit checking account with Amalgamated Bank.
\begin{enumerate}
\item The Board of Directors should authorize the opening of a bank account.
\item The Board of Directors should authorize all check signers.
\item The Board of Directors should authorize the closing of a bank account.
\item The Executive Director should share recommendations with the Board of Directors regarding these items
\end{enumerate}
\end{enumerate}
\item Contracts Policy
\begin{enumerate}
\item Contracts must be signed by the Executive Director, or President of the Board
\item Contracts signed by any other staff member will not be considered valid
\end{enumerate}
\item Accounting System
\begin{enumerate}
\item The financial statements should be prepared on an accrual basis of accounting in accordance with the reporting requirements of Generally Accepted Accounting Principles for organizations $($GAAP$)$ as found in Statement of Financial Accounting Standards.
\item Fiscal Year End: The organization has elected January 1 through December 31 as its fiscal year.
\item Fund accounting is a means of segregating assets into their categories of unrestricted, temporarily restricted, or permanently restricted. 
\begin{enumerate}
\item  {\it Restricted funds} (temporary and permanent) are funds that must be used for specific purposes, contracts, or line items. These restrictions are primarily imposed by grant-makers or investors.
\item {\it Unrestricted funds} are those in the General Operating fund that are not tied to any individual line items in the Operating fund and may be used at least from the perspective of the external funding sources for general support of the organization. 
\end{enumerate}
\item The Executive Director/Accountant is responsible for ensuring the proper recording and classification of all revenues, expenses, assets, liabilities and fund balances. The Executive Director/Accountant will ensure the proper recording and classification by properly maintaining the Chart of Accounts of the General Ledger and overseeing account setup and the assignment of attributes to accounts.
\begin{enumerate}
\item The Chart of Accounts is structured to facilitate preparation of financial statements. Account attributes will be assigned based on classification $($revenues, expenses, assets, liabilities and fund balances$)$ as well as by functional classification $($business unit$)$.
\item The General Ledger is a detail of activity of all accounts.  It is maintained using accounting software $($Quickbooks$)$. All input and balancing is the responsibility of the Accountant with final approval of the Executive Director.
\end{enumerate}
\item Unusual Transactions
\begin{enumerate}
\item The Executive Director should review the general ledger on a monthly basis for unusual transactions. 
\item The Executive Director should bring unusual transactions to the attention of the Board of Directors.
\end{enumerate}
\end{enumerate}
\item Revenue and Cash Receipts Policy
\begin{enumerate}
\item Bank deposits can be made by the Executive Director.
\item Once a contract is signed and adopted, expenditures are tracked in accordance with the contract and all reports and expenditures are submitted on a timely basis.
\item All cash received will be counted, verified, and signed off by the Executive Director and the Board of Directors. A receipt of the deposit will be kept for internal control purposes. Cash Receipts Form requires two signatures.
\end{enumerate}
\item Billing and Invoice Policy
\begin{enumerate}
\item The Executive Director/Accountant will receive, review and approve all invoices and bills, prepare “Requests for Payments” or “Requests for Reimbursements” for all invoices and bills, and review these requests and appropriate documentation with a member of the Finance Committee.
\item A member of the Board of Directors is responsible for approving all requests as identified in Revenue and Cash Receipts.
\item Checks without signatures are prepared by the Executive Director/Accountant. 
\item There are two check signatories, including Executive Director and one Board of Directors. Two signatures are required, or written acknowledgement of one signature must be recorded by both the Executive Director and Board of Directors.
\item All receipts must be submitted within 60 days of purchase to the Executive Director for reimbursement approval.
\end{enumerate}
\item Revenue Recognition
\begin{enumerate}
\item The organization’s revenue consists of grants, contributions and contracts from governments, foundations, organizations, corporations and individuals.
\begin{enumerate}
\item Grants, contracts contributions should be recognized in the accounting period when the grant is awarded or received. 
\end{enumerate}
\end{enumerate}
\item Fixed Assets
\begin{enumerate}
\item Fixed Assets consist of land, building, furniture, equipment, and vehicles costing \$500 or more. Such assets are capitalized and depreciated. Fixed assets under \$500 are expensed.
\item When depreciable assets are retired or otherwise disposed of, the cost and the resultant gain or loss is reflected in the current period.
\item Assets purchased with government grants shall be treated as expendable assets and recorded in the organization's Statement of Activities. The assets shall be appropriately marked as owned by a specific entity and properly numbered. The assets shall be returned to said entity at the end of the contract period.
\end{enumerate}
\item Purchasing and Disbursement of Funds Policy
\begin{enumerate}
\item Contractor bids will be reviewed and approved by the Executive Director with recommendations by the Board of Directors.
\item All purchases are approved by a signature and date on the purchase order, invoice or approval form with documentation attached. 
\end{enumerate}
\item Management of Accounts Payable, Cash Disbursements and Credit Card Management
\begin{enumerate}
\item Credit Card
\begin{enumerate}
\item The receipts for all credit card charges will be provided. The charges will be verified on the monthly statement when submitted.
\item All employee’s credit card usage will be provided to the Executive Director for review.
\item Issuance of employee credit cards must be approved by the Executive Director. Eligible expenditures must be preapproved by the Executive Director prior to incurring any charges.
\end{enumerate}
\end{enumerate}
\item Management of Employee Payroll
\begin{enumerate}
\item The Executive Director/Accountant will process bi- weekly payroll. Payroll is set up as direct deposit.
\item Forms W-2 are issued to employees in accordance with Internal Revenue Service guidelines.
\end{enumerate}
\item Policy for Financial Statements
\begin{enumerate}
\item The Finance Committee of the Board of Directors will meet monthly.
\item Financial Reports include year to date, budget vs. actual for the organization, expenditures, and budget vs actual by program. Explanations of overages or under budget line items are provided by the Executive Director.
\item The reports listed in last item will be shared and discussed monthly in the Board of Directors meetings. 
\item At the end of the month and fiscal year end, the Executive Director will review all balance sheet accounts.
\end{enumerate}
\item Financial Management Policy
\begin{enumerate}
\item Regen Foundation will contract with an outside firm to conduct an annual audit or review, as necessary, and required by law. 
\item The Department of Revenue of the State of Massachusetts determines the organization’s audit (attest) requirements. Management financial reports (unaudited) should be prepared and reviewed quarterly by the Executive Director for the Board of Directors. 
\item The Executive Director prepares a draft annual budget for review by the Board of Directors in September/October. The draft will be reviewed by the Board of Directors and submitted for approval in October/November. 
\item The budget is formally reviewed mid-year for adjustments made with the approval of the Board of Directors. 
\item Regen Foundation will retain the internal bookkeeping services of Cohen \& Co.
\item All bank statements, checks, contracts, invoices and other financial documents related to Regen Foundation are stored in an online storage system in a secure manner. 
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{document}