\documentclass{article}
\usepackage{dirtytalk}
\usepackage{xcolor}
\usepackage{hyperref}
\begin{document}
\title{GRANT RESPONSIBILITY EXPENDITURE  AGREEMENT}
\author{Date: \textcolor{cyan}{\emph{insert date}}}
\date{} 
\maketitle
\par
\begin{flushleft}
Regen Foundation
\par
\textcolor{cyan}{\emph{Address}}
\end{flushleft}
\par
Dear \textcolor{cyan}{\emph{name of officer for grantee organization}}:
\par
This letter (this \say{Grant}) sets forth the agreement of \textcolor{cyan}{\emph{name of grantee organization}} (\say{Grantee}) with respect to a grant of \textcolor{cyan}{\emph{quantity of}} REGEN, the native token of Regen Network (the \say{Grant Funds}), proposed to be made by Regen Foundation (the “Foundation”) for \textcolor{cyan}{\emph{specifically describe the purposes of the grant (the \say{Charter})}}.
\par
Grantee agrees that it will not use any Grant Funds received from the Foundation for any of the following purposes:  to attempt to influence legislation or the outcome of any specific public election; to carry on, directly or indirectly, any voter registration drive; to make grants to individuals for travel, study or similar purposes unless the grant is made for a project undertaken under the supervision of your organization and your organization controls the selection of the individual grantee in compliance with section 4945(d)(3) of the Internal Revenue Code and the regulations thereunder; or to undertake any activities that are not charitable, scientific, literary, educational or necessary for the sustained integrity of the Grantee’s operations to achieve such charitable, scientific, literary or educational purpose.      
\par
Grantee understands that the Foundation is making this Grant only for the purposes stated in this letter and shall not transfer any interest in the Grant Funds. Grantee agrees to publish narrative and financial reports in ways accessible to the public, and notify the Foundation on the progress of the Grantee’s organizational goals at the end of each fiscal year \textcolor{cyan}{\emph{specify fiscal year end}} . Grantee agrees to publish such reports within three months after the completion of Grantee’s fiscal year and notify the Foundation of their publication.  These  reports will cover all expenditures made by the Grantee for such fiscal year (including, but not limited to, salaries, travel, and supplies) and shall be published within a reasonable time after each fiscal year. For public disclosures, precautions can be taken to anonymize or pseudonymize personal expenses and other potentially sensitive information, although this information is still required to be reported to the Foundation.  Grantee understands that each report must include a narrative account of what was accomplished by Grantee’s expenditure of funds (including a description of progress made towards achieving the goals of the Grant), a financial statement as described below, and copies of any publications resulting from the Grant. Grantee agrees that the financial statement will be attested to by the responsible financial officer of Grantee or a certified public accountant, and will reflect the categories stipulated in the attached budget. 
\par
Grantee acknowledges that all payments of Grant Funds will be locked up in accordance with the applicable vesting schedule. Grantee agrees to keep records of receipts and expenditures under the grant, as well as copies of reports submitted to the Foundation, for at least four years following completion of such receipts and expenditures. Grantee agrees to make its books and records available for the Foundation’s inspection upon request Grantee agrees to make its books and records available for the Foundation’s inspection upon request.
\par
Grantee agrees to permit the Foundation access from time to time in order to conduct an evaluation of operations under this Grant, which may include a visit by Foundation personnel to review records and materials connected with the activities financed by this Grant. The Grantor may use imagery derived from such visits for use in promotional materials with the prior written consent of Grantee.
\par
Grantee certifies that it has reviewed (1) the Department of the Treasury’s Office of Foreign Assets Control \href{https://www.treasury.gov/resource-center/sanctions/SDN-List/Pages/default.aspx}{Specially Designated Nationals List}, which will identify entities designated by the U.S. Government as Foreign Terrorist Organizations or as supporters of terrorism, (2) the U.S. Government's \href{https://www.state.gov/j/ct/rls/other/des/123086.htm}{Terrorist Exclusion List} maintained by the Department of Justice, the list promulgated by the United Nations pursuant to U.N. Security Council Resolutions \href{https://www.un.org/sc/suborg/en/sanctions/1267/aq_sanctions_list}{1267} and \href{https://www.un.org/en/ga/search/view_doc.asp?symbol=S/RES/1390(2002)}{1390}, and the list promulgated by the European Union pursuant to EU Regulation \href{https://www.loc.gov/law/help/EUTerroristLists.pdf}{2580} (collectively, \say{the lists}). Grantee certifies that it does not employ or deal with (1) any individuals or entities the lists or (2) any individuals or entities that support terrorism. Grantee agrees to take reasonable steps and precautions to ensure that Grant Funds provided by the Foundation are not ultimately distributed to terrorist organizations or individuals that support terrorism, including any organization or individual identified on the lists. Reports of steps and precautions taken to meet this goal must be provided to the Foundation upon request.
\par
Grantee must inform the Foundation immediately of significant changes in its registration status, tax-exempt status, governance, jurisdiction, name, location, projects, goals and activities.
\par
Grantee understands that the foregoing conditions comply with the Foundation’s obligation under U.S. law to make reasonable efforts and establish adequate procedures to see that Grant Funds are awarded in accordance with U.S. laws, and to maintain full and complete records on how Grant Funds have been awarded. Grantee understands that changes in U.S. laws, or in regulations interpreting U.S. laws, may require the Foundation to ask Grantee to submit more detailed reports or to take other steps. Grantee understands that the Foundation would promptly inform Grantee of any such changes, and Grantee agrees to comply with any such additional requirements.  Grantee agrees that the Foundation may, in its sole discretion, discontinue funding if it is not satisfied with the progress of the grant or the content of any written report.
\par
Grantee acknowledges that the Foundation is unable to recover lost REGEN wallets. It is the Grantee’s responsibility to manage adequate security practices, although the Foundation is available to advise on certain best practices.
\par
Grantee acknowledges that delegated tokens are subject to \say{slashing} if their validator double-signs transactions or has downtime. Only delegated tokens can participate in governance and earn block rewards.
\par
Grantee acknowledges that it is expected to take a \say{built in public} approach in pursuit of some subset of the charitable mission of the Foundation. If the Foundation deems the Grantee is in breach of the \say{built in public} approach and/or this Grant, the Foundation reserves the right to publish such breach or initiate a community process to bring the issue to a token holder governance vote (with or without the prior approval of the Regen Consortium) to determine whether or not the Foundation will revoke this Grant and recover the Grant Funds.
\par
Grantee understands that the Foundation will include information on this Grant in its periodic public reports.
\par
\begin{flushright}
Very truly yours,
\par
\textcolor{cyan}{\emph{signature}}
\par
Name: Revathi Kollegala
\par
Title: Executive Director
\end{flushright}
\par
Attachments
\end{document}