\documentclass[10pt]{article}
\usepackage[usenames]{color} %used for font color
\usepackage{amssymb} %maths
\usepackage{amsmath} %maths
\usepackage[utf8]{inputenc} %useful to type directly diacritic characters
\begin{document}
\title{TOKEN OWNERSHIP \& TRADING POLICY \protect\\ OF \protect\\ REGEN FOUNDATION}
\author{Adopted: June 1st, 2021 by the Board of Directors}
\date{} 
\maketitle
\begin{enumerate}
\item \underline{Purpose}
  \begin{enumerate}
  \item The purpose of this Token Ownership \& Trading Policy (“{\bf Policy}”) is to describe the ownership, trading and restricted use of Material Nonpublic Information (as defined below) relating to Regen Foundation and its affiliates. Additionally, this Policy seeks to protect any confidential and price-sensitive information to ensure that the market for \$REGEN tokens remains transparent and therefore trading of \$REGEN tokens fosters fair trading for all participants.
  \end{enumerate}
\item \underline{Token Ownership}
  \begin{enumerate}
  \item Regen Foundation (the “{\bf Foundation}”) is one of the major token holders in the Regen Network (“{\bf RN}”) ecosystem, having 5mm \$REGEN tokens in its endowment and stewarding 30mm \$REGEN tokens for Community Staking DAOs (with a total supply close to 100mm \$REGEN tokens at launch).
  \item In the Foundation’s July 2020 correspondence with the United States Internal Revenue Service (“{\bf IRS}”), the Foundation disclosed that two of its Board Directors already held tokens, and charitable status was approved without further questions regarding this issue.
  \item Given this context, the Foundation does not have any prohibition against directors, officers, employees, or other involved parties owning \$REGEN tokens, as this does not contribute to any misalignment of incentives.
  \end{enumerate}
\item \underline{Token Trading}
  \begin{enumerate}
  \item As a decentralized token, the Foundation cannot control the flow of \$REGEN tokens within the ecosystem. That said, the following policy applies to the Foundation insiders, and the Foundation will use its best efforts to prevent trading that could violate state and federal securities laws including federal insider trading law. In summary, insider trading law seeks to prohibit trading by individuals with access to confidential or non-public information about the subject company that is beneficial to insiders or could result in price manipulation.
  \item {\bf Insiders} are defined by team members (employees, contractors, board members, advisors, etc.) that have access to non-public material information regarding the Foundation.
  \item {\bf Material information} is defined as information that could reasonably be assumed to influence the token price or that there is a substantial likelihood a reasonable individual would consider the information important in making a decision to buy or sell \$REGEN tokens.
  \item {\bf Nonpublic information} is defined as information that has not been disclosed generally to the public. Information will be considered {\bf public} if it is published on the Foundation’s website, Twitter, Discord, email newsletter, or other public official channels.
	\end{enumerate}
\item \underline{Trading Dark Periods}
	\begin{enumerate}
	\item Under certain circumstances, the Foundation may impose a period of absolute prohibition on the trading of \$REGEN tokens (“{\bf Dark Period}”) as a result of events deemed materially significant by the Foundation’s board of directors (the “{\bf Board}”), in their sole discretion. Further, Insiders will be notified of Dark Periods and the specific blackout periods applicable. All Dark Periods will be managed in all respects by the Board.
	\item Additionally, any Insider shall refrain from buying or selling \$REGEN tokens during time periods when such Insider is aware of any Material Nonpublic Information regarding the Foundation. This prohibition on trading will expire 48 hours subsequent to public disclosure.
	\item Insiders must use their best judgement to determine when these time periods begin and end, based on the above criteria, but the following serve as text-book examples to illustrate time periods when insider trading would be prohibited:
		\begin{enumerate}
		\item The \$REGEN token becomes subject to an investigation by the United States Securities and Exchange Commission that has not yet been publicized.
		\item \$REGEN tokens will be listed on a major exchange, and such listing has not yet been publicized.
		\item Regen Ledger is preparing to launch a major new feature set, and such feature launch has not yet been publicized.
		\end{enumerate}
	\item Exceptions to Dark Periods:
		\begin{enumerate}
		\item The restrictions set out in this Policy do not apply in cases where the Foundation notifies Insiders of specific guidelines and instructions regarding the trading of \$REGEN tokens pursuant to any token distribution scheme, or similar instrument, launched by the Foundation following the distribution of any \$REGEN tokens to Insiders and/or associates.
		\end{enumerate}
	\end{enumerate}
\item \underline{Who to Contact}
	\begin{enumerate}
	\item Insiders with any questions or information to report regarding any transaction involving Material Nonpublic Information to the President of the Board.
	\end{enumerate}
\end{enumerate}
\end{document}